Predicting the 2024 US Presidential Election with a Model-Based Forecast

### 2024-11-03 paper/paper.qmd
update Appendix B

### Stratification variables 
* Age: 18-29, 30-44, 45-64, 65+
* Gender: Male, Female, Non-binary
* Race: White, Black/African American, Hispanic/Latino, Asian, Native, Other
* Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other
* Geographic region: Northeast, Midwest, South, West
* Political Party: Democratic, Republican, Independent, Other

@@

4.What is your age?\
* 18-24 / 25-34 / 35-44 / 45-54 / 55+\
5.What is your gender?\
* Male / Female / Non-binary / Prefer not to say\
6.Which of the following best describes your education level?\
* High School / Some College / Bachelor's Degree / Graduate Degree / Other\
7.Which region of the U.S. do you currently reside in?\
* Northeast / Midwest / South / West\    
8.Do you generally identify with a political party?\
* Democratic / Republican / Independent / None

@@

9.How likely are you to participate in the upcoming presidential election?\
* Very Likely / Somewhat Likely / Not Sure / Unlikely / Very Unlikely\
10.If the presidential election were held today, for which candidate would you vote?\
* Kamala Harris (Democrat) / Donald Trump (Republican) / Undecided / Prefer not to say\
11.What are the top three issues that will influence your vote?\
* Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]

@@

12.Which of the following sources do you rely on most for political news and information?\
* Television News / Newspapers / Online News Websites / Social Media / Radio / Friends and Family / Other\
13.How often do you engage in discussions about political topics with friends or family?\
* Daily / Weekly / Monthly / Rarely / Never

@@

14.Please select 'Agree' to verify that you are paying attention.\
* Agree / Disagree\
15.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
* Yes / No

>>>>

### Stratification variables 
* Age: 18-29, 30-44, 45-64, 65+
* Gender: Male, Female, Non-binary
* Race: White, Black/African American, Hispanic/Latino, Asian, Native, Other
* Income Level: <$30,000,  \$30,000-\$59,999, \$60,000-\$99,999, >\$100,000
* Education level: High School, Some College, Bachelor's Degree, Graduate Degree, Other
* Geographic region: Northeast, Midwest, South, West
* Political Party: Democratic, Republican, Independent, Other

@@

4.What is your age?\
* 18-24 / 25-34 / 35-44 / 45-54 / 55+\
5.What is your gender?\
* Male / Female / Non-binary / Prefer not to say\
6.Which of the following best describes your race or ethnicity?
* White / Black / African American / Hispanic or Latino / Asian / Native / Other\
7.Which of the following best describes your education level?\
* High School / Some College / Bachelor's Degree / Graduate Degree / Prefer not to say/ Other\
8.What was your family/individual income last year?
* <$30,000 / \$30,000-\$59,999 / \$60,000-\$99,999 / >\$100,000 / Prefer not to say\
9.Which region of the U.S. do you currently reside in?\
* Northeast / Midwest / South / West\    
10.Do you generally identify with a political party?\
* Democratic / Republican / Independent / None / Prefer not to say

@@

11.How likely are you to participate in the upcoming presidential election?\
* Very Likely / Somewhat Likely / Not Sure / Unlikely / Very Unlikely\
12.If the presidential election were held today, for which candidate would you vote?\
* Kamala Harris (Democrat) / Donald Trump (Republican) / Undecided / Prefer not to say\
13.What are the top three issues that will influence your vote?\
* Economy / Healthcare / Education / Gun Policy / Taxes / Foreign Policy / Social Security / Civil Rights / Technology / Privacy / Other[text]

@@

14.Which of the following sources do you rely on most for political news and information?\
* Television News / Newspapers / Online News Websites / Social Media / Radio / Friends and Family / Other\
15.How often do you engage in discussions about political topics with friends or family?\
* Daily / Weekly / Monthly / Rarely / Never

@@

16.Please select 'Agree' to verify that you are paying attention.\
* Agree / Disagree\
17.Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
* Yes / No
